\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{placeins}
\usepackage{listings, lstautogobble}
\lstset{basicstyle=\ttfamily}

\title{Final Project Charter}
\author{Alex Libman (asl237), Jacob Glueck (jng55), \\Amit Mizrahi (am2269), Siddant Basnet (sb846)}
\date{}

\begin{document}
\maketitle

\section{Meeting Plan}
We plan to meet regularly on Tuesday nights at 2000 hours, and Saturdays at 1900 hours. 

\section{Proposal}
\subsection{Vision}
A peer-to-peer encrypted messaging system designed for communication between people on the same network.

\subsection{Key Features}
\begin{itemize}
	\item UDP based discovery of other connected users on the same network 
	\item Encrypted messaging over TCP using the RSA algorithm
	\item Group messaging
	\item Ability to load missed messages from peers in the same group
	\item Ability to set a username
	\item Can export chat log to .txt file
\end{itemize}

\subsection{Description}
A sample user starts the program and has the option to send out a UDP broadcast to discover other online users on the same network. This lists the IP addresses, user names, and public keys of these connected users. The user can choose to message any number of these users, creating a group messaging session. The other users in this newly formed group receive a notification, inviting them to join the conversation. Once they do so, they will be able to send messages to everyone else who has agreed to join the group. If a user logs off and then logs back into a session, the client will request all of its peers for a history of what has happened during the logged-off period.

All messages sent using this system will be encrypted and signed using RSA. Every user will maintain a keychain mapping usernames to public RSA keys. Every time a user starts a chat, the program will verity that the public key and username pair advertised with the chat matches that stored in the user's local keychain (this is a very simplified version of the PGP trust model.) For group messages, each client will encrypt his message with the public keys of all the other peers, and he will sign it with his private key. Upon receiving a message, all clients will verify the signature.

\subsection{Sample Session}
\begin{lstlisting}
> :discover

IP Address		Username	RSA Fingerprint
192.168.4.7		libman		4E8D A652 8149 72C7 ...
192.168.16.3		sid		E4A7 2584 62C7 3274 ...

> :message libman sid

Creating group...
Warning: Fingerprint for `libman` 
does not match fingerprint found in keychain.
Are you sure you wish to proceed? (Y/n) y

Session started. Session UUID: 4b4e24c3-aa5c-42cf-8f0d-3187948201a3

system: @libman (192.168.4.7) has connected.
system: @sid (192.168.16.3) has connected.
libman: what's up
sid: hi

> hello!
		

\end{lstlisting}

\end{document}